---
title: "Evaluate Reproducibility"
author: "Rob Carnell"
date: "5/31/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(foreign)
require(assertthat)
```

## Modifications and Order of operations

1. Change the Stata working directory to `/scripts`
2. Run `/scripts/surname_creation_lower.do`
    - Changed output file name to be compared to original
    - Creates `/input_files/created/census_surnames_lower_check.dta`
3. Run `/scripts/create_attr_over18_all_geo_entities.do`
    - Changed output file name to be compared to the original
    - Creates
        - `/input_files/created/blkgrp_attr_over18_check.dta`
        - `/input_files/created/tract_attr_over18_check.dta`
        - `/input_files/created/zip_attr_over18_check.dta`
4. Create output directory
5. Run `/scripts/create_test_data.do`
    - Changed output file for consistency
    - Creates `../output/fictitious_sample_data_check.dta`
6. Edit `/scripts/combine_probs.do`
    - Change output file and the Stata version to 12
    - Creates `test_proxied_final.dta`
7. Run `/scripts/main_test_data.do`
    - Changed file name from `fictitious_sample_data` to `fictitious_sample_data_check`
    in multiple places
    
## File Comparisons

```{r}
created_dir <- file.path("..", "input_files", "created")
standard <- foreign::read.dta(file.path(created_dir, "census_surnames_lower.dta"))
repro <- foreign::read.dta(file.path(created_dir, "census_surnames_lower_check.dta"))
assertthat::assert_that(nrow(repro) == 167409)

standard2 <- foreign::read.dta(file.path(created_dir, "blkgrp_attr_over18.dta"))
repro2 <- foreign::read.dta(file.path(created_dir, "blkgrp_attr_over18_check.dta"))
assertthat::assert_that(all(standard2$GeoInd == repro2$GeoInd))
assertthat::assert_that(all(abs(standard2$geo_pr_white[!is.na(standard2$geo_pr_white)] - repro2$geo_pr_white[!is.na(repro2$geo_pr_white)]) < 1E-6))

standard3 <- foreign::read.dta(file.path(created_dir, "tract_attr_over18.dta"))
repro3 <- foreign::read.dta(file.path(created_dir, "tract_attr_over18_check.dta"))
assertthat::assert_that(all(standard3$GeoInd == repro3$GeoInd))
assertthat::assert_that(all(abs(standard3$geo_pr_white[!is.na(standard3$geo_pr_white)] - repro3$geo_pr_white[!is.na(repro3$geo_pr_white)]) < 1E-6))

standard4 <- foreign::read.dta(file.path(created_dir, "zip_attr_over18.dta"))
repro4 <- foreign::read.dta(file.path(created_dir, "zip_attr_over18_check.dta"))
assertthat::assert_that(all(standard4$GeoInd == repro4$GeoInd))
assertthat::assert_that(all(abs(standard4$geo_pr_white[!is.na(standard4$geo_pr_white)] - repro4$geo_pr_white[!is.na(repro4$geo_pr_white)]) < 1E-6))
```

- `census_surnames_lower.dta`
    - Repository File:  `r dim(standard)`
    - Reproduction: `r dim(repro)`
        - According the project README, 167,409 entries were expected.  The repository file was not updated
        when the 2017 update was released.  Two columns were also added in the 2017 update.
- `blkgrp_attr_over18.dta`
    - Repository File:  `r dim(standard2)`
    - Reproduction: `r dim(repro2)`
- `tract_attr_over18.dta`
    - Repository File:  `r dim(standard3)`
    - Reproduction: `r dim(repro3)`
- `zip_attr_over18.dta`
    - Repository File:  `r dim(standard4)`
    - Reproduction: `r dim(repro4)`

```{r}
rm(standard, repro, standard2, repro2, standard3, repro3,
   standard4, repro4)
```

```{r}
output_dir <- file.path("..", "output")
repro <- foreign::read.dta(file.path(output_dir, "test_proxied_final.dta"))
standard <- read.csv(file.path("..", "test_output", "test_proxied_final.csv"))
assertthat::assert_that(all(abs(standard$pr_white - repro$pr_white) < 1E-6))
assertthat::assert_that(all(abs(standard$name_pr_black - repro$name_pr_black) < 1E-6))
fict <- foreign::read.dta(file.path(output_dir, "fictitious_sample_data_check.dta"))
assertthat::assert_that(all(fict$geo_code_precision == standard$geo_code_precision))
```

## R project validation

Now to validate the R project, we need to be able to produce the same artifacts.



